\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2014-09-30 paper2015asml.tex
less verbose control question

In addition to the rating and demographic questions, a control question was incorporated to account for satisficing in online surveys~\cite{krosnick1991response}~\cite{krosnick1996satisficing}. This question served as the first counter-measure against satisficing in the survey. It asked the participant to correctly answer a question about the robot performing a simple, and easy-to-recognize motion.

The other counter-measure was to manually inspect the responses, and assess whether it agrees with the other survey respondents on a participant-by-participant and then trajectory-by-trajectory basis. The process for examining a particular participant involves seeing how his/her ratings {\em agree or disagree} with the average ratings of all the other ratings for this particular trajectory. Aggregating this over all the trajectories the participant rated gives us an idea of how much we can trust their responses and make a decision about rejecting {\em all or none} of their responses.

Another heuristic we employed in inspecting the responses was looking for the average time to complete the survey to be extremely low, which could hint at strong satisficing.

>>>>

In addition to the rating and demographic questions, a control question was incorporated to account for satisficing in online surveys~\cite{krosnick1991response}~\cite{krosnick1996satisficing}. Also we manually inspect the responses, and assess whether it agrees with the other survey respondents on a participant-by-participant and then trajectory-by-trajectory basis. We also look at the time to complete the survey as another indicator for satisficing.
